Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

Looks through the training data and compiles a list of most common words for
each item in the data. When the test data is run, the feature looks for the
created vector and uses that instead of trying to make a new one. Next the
extractor takes a window of words around the head word and generates the 0, 1
tuple of features for inclusion to the dictionary. This word list is used as the
keys of the feature vector when using the test data as a list of words that may
cooccur with each item in the data. The value associated with each key in the
feature vector starts out as 0 (for occurring 0 times in the window near a test
word) If a key in the feature vector does occur with a word in the test data,
the value associated with the key changes to 1 even if the key occurs more than
once.  This is necessary because the machine learning algorithm we used does not
attempt to analyze the keys beyond simple equality, so higher numbers than one
could have masked the possibly more important distinction between 0 and not-0.
In other words, keeping track of the instances of occurrence vs clustering them
into 2 groups reduces the sparsity of the data and allows for a higher chance of
accurate classifications based on the limited training data that we have. This
is an especially important consideration since the feature vectors that select
the most common words by looking through all the instances of unique lexical
items in the training data are unsupervised.

>>>>

Looks through the training data and compiles a list of most common
words for each item in the data in the form of a vector. When the test
data is run, the feature looks for the previously made vector and uses that instead of
trying to make a new one. Next the extractor takes a window of words
around the head word and generates the 0, 1 tuple of features for
inclusion to the dictionary. This list constitues the features in the
feature vector rather than the list of common words. The value
associated with each key in the feature vector starts out as 0 (for
occurring 0 times in the window near a test word) If a key in the
feature vector does occur with a word in the test data, the value
associated with the key changes to 1 even if the key occurs more than
once.  This is necessary because the machine learning algorithm we
used does not attempt to analyze the keys beyond simple equality, so
higher numbers than one could have masked the possibly more important
distinction between 0 and not-0. In other words, keeping track of the
instances of occurrence vs clustering them into 2 groups reduces the
sparsity of the data and allows for a higher chance of accurate classifications
based on the limited training data that we have. This is an especially
important consideration since the feature vectors that select the most
common words by looking through all the instances of unique lexical
items in the training data are unsupervised.
